\documentclass[letterpaper,12pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{graphicx}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{1pt}
\input{glyphtounicode}

\RequirePackage{tikz}
\RequirePackage{xcolor}

\definecolor{cvblue}{HTML}{0E5484}
\definecolor{darkcolor}{HTML}{0F4539}
\definecolor{cvgreen}{HTML}{3BD80D}
\definecolor{taggreen}{HTML}{00E278}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\colorlet{name}{black}
\colorlet{tagline}{darkcolor}
\colorlet{heading}{darkcolor}
\colorlet{headingrule}{cvblue}
\colorlet{accent}{darkcolor}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

\usepackage[scaled]{helvet}
\renewcommand\familydefault{\sfdefault}
\usepackage{fontawesome}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.2in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}
\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{cvblue}\titlerule \vspace{-6pt}]

\pdfgentounicode=1

% Custom commands
\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\circ$}

\newcommand{\resumeItem}[1]{
  \item\small{#1 \vspace{-4pt}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{0pt}\item
  \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{#3} & \textit{#4} \\
  \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.5in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-8pt}}

% Document starts here
\begin{document}

%----------HEADING----------
\begin{center}
    {\huge \textbf{MD Piyal Ahmmed}} \\[2pt] 
    \vspace{1em}
    \faPhone\ {(+88) 01880288682} ~ 
    | ~
    \faEnvelope\ \href{mailto:piyalahmmed01@gmail.com}{\color{blue}\textbf{piyalahmmed01@gmail.com}} ~ 
    | ~
    \faLinkedin\ \href{https://www.linkedin.com/in/md-piyal-ahmmed-bb1033205/}{\color{blue}\textbf{MD Piyal Ahmmed}} ~
    | ~
    \faGithub\ \href{https://github.com/piyal21}{\color{blue}\textbf{Piyal}} ~
    \vspace{-8pt}
\end{center}

%-----------EDUCATION-----------
\vspace{4pt}
\section{\color{cvblue}\faGraduationCap~ EDUCATION}
\resumeSubHeadingListStart
  \resumeSubheading
    {Ahsanullah University of Science and Technology}{Dhaka, Bangladesh}
    {Bachelor of Science in Computer Science and Engineering}{2025}

  % \resumeSubheading
  %   {Birshreshtha Noor Mohammad Public College}{Dhaka, Bangladesh}
  %   {Higher Secondary Certificate}{2019}
\resumeSubHeadingListEnd


%-----------WORKING EXPERIENCE-----------
\section{\color{cvblue}\faBriefcase~ WORKING EXPERIENCE}

\resumeSubHeadingListStart
  \resumeSubheading
    {Gigabit}{Dhaka, Bangladesh}
    {Junior AI Engineer}{OCT 2025 -- Present}
  \resumeItemListStart
    \resumeItem{Developed and optimized machine learning pipelines for AI-driven automation and intelligent data processing.}
   \resumeItem{Implemented Retrieval-Augmented Generation (RAG) systems integrating vector databases and LLMs for improved contextual accuracy in AI applications.}
   
  \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------RESEARCH EXPERIENCE-----------
\section{\color{cvblue}\faFlask~ RESEARCH EXPERIENCE}
\resumeItemListStart
  \resumeItem{\normalsize{\textbf{Gender Bias Mitigation for Bangla Classification Tasks} | \href{https://arxiv.org/html/2411.10636v1}{\color{blue}\underline{Link}}}}
  \resumeItemListStart
    \resumeItem{Developed four manually annotated datasets for sentiment analysis, toxicity detection, hate speech detection, and sarcasm detection in Bangla.}
    \resumeItem{Used a gender-name swapping method to detect gender bias in pretrained models.}
    \resumeItem{Evaluated on Bangla BERT-based models and achieved improved fairness without compromising accuracy.}
  \resumeItemListEnd
\resumeItemListEnd

%-----------PROJECTS-----------
\section{\color{cvblue}\faCode~ PROJECTS}
\resumeItemListStart
  \resumeItem{\normalsize{\textbf{AI-Powered Question Answering System} | \href{https://github.com/piyal21/10MS_ML_Assessment}{\color{blue}\underline{Link}}}}
  \resumeItemListStart
    \resumeItem{Developed an AI-driven question-answering tool using OpenAI embeddings and FAISS for fast, accurate semantic search over large datasets.}
    \resumeItem{Integrated OpenAI GPT models to generate contextually relevant and precise answers based on vector search results.}
    \resumeItem{Built an interactive UI with Streamlit for visualization.}

  \resumeItemListEnd

  \vspace{1em}

  \resumeItem{\normalsize{\textbf{Intelligent Content Generator} | \href{https://github.com/piyal21/Gen-AI-Projects/tree/master}{\color{blue}\underline{Link}}}}
  \resumeItemListStart
    \resumeItem{Built an automated content generation tool mimicking LinkedIn influencers’ writing style using few-shot prompting.}
    \resumeItem{Developed an interactive UI using Streamlit for selecting post topic, tone, and length with real-time preview.}
    \resumeItem{Integrated OpenAI’s LLM backend to ensure high-quality, stylistically aligned post generation.}
  \resumeItemListEnd
\resumeItemListEnd

%-----------TECHNICAL SKILLS-----------
\section{\color{cvblue}\faTools~ TECHNICAL SKILLS}
\begin{multicols}{2}
\resumeItemListStart
  \resumeItem{\textbf{Programming Languages:} Python, C++, Java}
  \resumeItem{\textbf{Libraries \& Frameworks:} PyTorch, TensorFlow, Scikit-learn, Pandas, NumPy, Transformers, LangChain, LangGraph, LangSmith}
  \resumeItem{\textbf{Machine Learning Techniques:} Deep Learning, Artificial Neural Networks (ANN), Convolutional Neural Networks (CNN), Natural Language Processing (NLP), Prompt Engineering, Retrieval-Augmented Generation (RAG), Fine-tuning}
  \resumeItem{\textbf{Databases:} MySQL, PostgreSQL}
  \resumeItem{\textbf{API Development:} FastAPI, REST API}
  \resumeItem{\textbf{Tools \& Platforms:} Git, Docker, MLflow, Jupyter Notebook}
  \resumeItem{\textbf{Concepts:} Data Structures, Algorithms, Object-Oriented Programming (OOP), Data Preprocessing, Feature Engineering, Model Evaluation Metrics}
\resumeItemListEnd
\end{multicols}

\end{document}